Quantifying social distancing behaviour across Australia in response to COVID-19

### 2020-04-28 manuscript/ms.Rmd
add NBN data section to mt_nbn branch

@@

>>>>

<!-- the shifts can be a sum, the bumps should be singular -->

@@

### Data

#### NBN

The National Broadband Network Co. (NBN) is the Australian national wholesale open-access data network, providing broadband access to retail service providers. The majority of its traffic is through wired broadband connections. As such, these connections are static in place, and they offer internet access to a broad mixture of users. NBN provided a time series (with a temporal resolution of 15 minutes) to aggregated data relating to mean upload and download traffic volume generated by houshold customers, aggregated spatiall by ABS Statistical Area 2 (SA2) region, and excluding data points generated by less than 600 customers.
